\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.3in,right=0.3in,bottom=0.2in,top=0.2in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-15pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Andy Kumeda}}\\
	Los Angeles, California $\cdot$ andy@kumeda.com $\cdot$ (310) 493-1793 $\cdot$ https://andykumeda.com\\
\end{center}

\header{Summary}
\vspace{1mm}

As an engineering and project management professional with over 25 years of hands-on technology experience, I am adept at operating across various hardware and software platforms. I excel in identifying and mitigating complex technology and business challenges, providing timely solutions while working within tight timelines and budgetary constraints. With a proven track record of success, I have designed and implemented large-scale enterprise server and networking infrastructures, providing both scalability and redundancy across multiple data center locations.

\vspace{1mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Delta9 Technology, LLC} \hfill Los Angeles, CA\\
\textit{Principal Consultant} \hfill 2017 - present\\
\vspace{-1mm}

\begin{itemize} \itemsep 1pt
\item Designed and implemented SolarWinds network performance monitoring and management solutions for a large-scale medical service provider, resulting in enhanced network visibility and proactive issue resolution.
	\item Successfully executed network architecture designs, incorporating IPS/IDS, firewall, and VPN appliances that adhered to FBI CJIS policies and FIPS 140-2 data encryption requirements, for local law enforcement agencies.
	\item Played a pivotal role in identifying, protecting, and managing corporate assets by monitoring and responding to security incidents in line with organizational policies and procedures.
	\item Designed and established critical business requirements for high-tech startups, meeting aggressive budget and timeline goals.
	\item Instituted a real-time application and infrastructure monitoring and alerting framework for a large multimedia and entertainment corporation, boosting operational efficiency and minimizing downtime.
	\item Delivered high-availability storage area networks and VM platform design development and procurement reports for multiple universities and outreach centers spanning across multiple campuses.
	\item Devised comprehensive system and network specifications, integration, project management, and test plans for mergers and acquisitions, streamlining the entire process and ensuring seamless transitions.
\end{itemize}
\textbf{DexYP} \hfill Dallas, TX\\
\textit{Architect} \hfill 2015 - 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Collaborated effectively with all stakeholders to implement comprehensive threat detection and prevention strategies, incident response plans, forensic analysis, and data loss prevention measures.
	\item Designed and produced innovative enterprise solutions involving WAN/LAN, WLAN, Data Analytics, Security, and Virtual (e.g., NFV, SDN) technologies, developing automation rules and management policies to streamline processes and boost efficiency.
	\item Worked closely with the executive team to conduct risk assessments and develop business continuity plans to ensure compliance with SOX and PCI requirements.
	\item Collaborated with internal customers and corporate leadership to analyze, research, and implement enterprise-wide network and security architecture solutions that aligned with business objectives and goals.
	\item Designed and developed a custom open-source DCIM application that integrated internal infrastructure and application databases, enabling accurate inventory and physical location tracking across multiple data centers.
	\item Provided expert guidance to ensure emerging technologies and innovative ideas were aligned with the enterprise\textquotesingle{}s operational and strategic goals, helping to drive overall success and growth.
	\item As a technology liaison leader, facilitated collaboration and integration of impactful and advanced technical solutions to drive enterprise-wide transformation and success.
\end{itemize}
\textbf{YP} \hfill Glendale, CA\\
\textit{Executive Director, Network \& Telecom} \hfill 2012 - 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Reviewed the performance of network and telephony resources to determine operating costs, productivity levels, and necessary upgrades, ensuring optimal use of resources while minimizing expenses.
	\item Planned and executed business requirements, managed projects, and allocated resources effectively for network and telephony infrastructures, driving successful outcomes and meeting project goals and objectives.
	\item Defined and communicated project milestones, service level agreements, and resource allocation to all relevant stakeholders, including the executive team, department leads, support staff, and end-users, ensuring everyone was aligned with project objectives and timelines.
\end{itemize}
\textbf{AT\&T Interactive} \hfill Dallas, TX\\
\textit{Associate Director, Voice \& Data} \hfill 2009 - 2012\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Presented compelling business case justifications and conducted thorough cost/benefit analyses for various operations spending and initiatives, ensuring informed decision-making by the executive team.
	\item Conducted benchmarking and analysis of the telephony and networking infrastructures to determine operating costs, productivity levels, and upgrade requirements, enabling informed resource allocation and strategic planning.
	\item Designed and implemented large-scale multi-vendor data and voice networks across multiple data centers, ensuring robust and scalable infrastructures that met business requirements and goals.
	\item Built and/or expanded six Tier 4 high-density data centers within the allocated budget and timeline, demonstrating strong project management skills and a deep understanding of data center technologies and requirements.
\end{itemize}
\textbf{Yellowpages.com \textbar{} AT\&T} \hfill Dallas, TX\\
\textit{Manager, Network Operations} \hfill 2007 - 2009\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Provided oversight for all network operations, remote communications, wide and local area networks within multiple data centers, ensuring reliable and secure network connectivity across the enterprise.
	\item Maintained and managed operational metrics, goals, and project timelines, providing visibility and transparency into network performance and project progress to relevant stakeholders.
	\item Ensured high availability and full redundancy for all network infrastructures to achieve 99.9\% uptime, minimizing downtime and maintaining business continuity.
	\item Managed and delivered large-scale projects utilizing technical analysis, data network planning, engineering, and global infrastructure design experience, achieving project success and delivering value to the organization.
\end{itemize}
\textbf{Curesearch \textbar{} National Childhood Cancer Foundation} \hfill Baltimore, MD\\
\textit{Director, Information Technology} \hfill 2004 - 2007\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Provided strategic oversight for infrastructure and data operations, ensuring alignment with the business and scientific objectives of the organization.
	\item Formulated and deployed long-term strategic plans for acquiring and enabling efficient and cost-effective information processing and communication technologies, ensuring that technology investments were aligned with organizational goals and priorities.
	\item Directed research on potential technology solutions and implementations in support of new initiatives, opportunities, and procurement efforts, providing informed recommendations to the executive team and relevant stakeholders.
\end{itemize}
\textbf{Yahoo! \textbar{} Overture Services \textbar{} Goto.com} \hfill Pasadena, CA\\
\textit{Senior Network Engineer} \hfill 2001 - 2004\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed, integrated, and implemented networks and data centers across twelve countries, incorporating sales and customer service resources and production web-searching facilities, to enable efficient and scalable operations in multiple regions.
	\item Led the technology mergers and acquisitions migration and integration of FAST and AltaVista, ensuring seamless transitions and minimal disruption to operations.
	\item Collaborated with senior engineering team leads and executive management to develop technology and business roadmaps, providing efficient, scalable, cost-effective, and fault-tolerant network and systems infrastructures.
	\item Worked with project managers and internal customers to define proper deliverables, communicate expectations, and manage risks, ensuring timely delivery of milestones and objectives.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Cloud:                                       & AWS, Azure, Digital Ocean, CloudFlare                                                               \\
	Network Management:                          & Solarwinds Orion, ManageEngine OpManager, Zabbix                                                    \\
	DevOps:                                      & Ansible \textbar{} Terraform, Github \textbar{} git, Docker \textbar{} Vagrant \textbar{} Multipass \\
	Collaboration \textbar{} Project Management: & Asana, Notion, Trello, Smartsheet, Jira \textbar{} Confluence, Kanban \textbar{} Scrum              \\
	Security:                                    & Fortigate, Cisco ASA, Rapid7                                                                        \\
	OS \textbar{} Languages:                                   & Python, Javascript, Linux \textbar{} MacOS, PHP                                                                             \\
\end{tabular}
\vspace{2mm}



\header{Awards}
\textbf{Cisco Certified Internetwork Expert (CCIE \#3406)} \hfill Cisco Systems\\
CCIE Routing \& Switching, Written \& Lab \hfill 1997\\
\vspace*{2mm}
\textbf{Cisco Certified Internetwork Expert (CCIE) Re-certification} \hfill Cisco Systems\\
Security (2001), IP (2003), Routing \& Switching (2004,2007), VoIP (2009), Service Provider (2011), Data Center (2015)\\
\vspace*{2mm}
\textbf{AT\&T Service Excellence Award} \hfill AT\&T\\
IPV6 Implementation \hfill 2011\\
\vspace*{2mm}
\textbf{METRC Validated Software Provider} \hfill METRC\\
CA Department of Food \& Agriculture \textbar{} CA Department of Public Health \hfill 2019\\
\vspace*{2mm}
\textbf{Certified Enterprise Blockchain Professional (CEBP)} \hfill 101 Blockchains\\
101 Blockchains \hfill 2021\\
\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{California State University, Long Beach}\\
BS Computer Science and Engineering \hfill 1986 - 1992\\
\vspace{2mm}

\ 
\end{document}
