%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Andy} \headerlastnamestyle{Kumeda} \\
	\vspace{2mm}
	{\faEnvelope\ andy@kumeda.com} | {\faMobile\ (310) 493-1793} | {\faMapMarker\ Los Angeles, California} | {\faLink\ https://andykumeda.com}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Principal Consultant}
	{Delta9 Technology, LLC}
	{Los Angeles, CA}
	{2017-01-03 – present}
	{\begin{cvitems}
		\item {Successfully executed network architecture designs, incorporating IPS/IDS, firewall, and VPN appliances that adhered to FBI CJIS policies and FIPS 140-2 data encryption requirements, for local law enforcement agencies.}
		\item {Played a pivotal role in identifying, protecting, and managing corporate assets by monitoring and responding to security incidents in line with organizational policies and procedures.}
		\item {Designed and established critical business requirements for high-tech startups, meeting aggressive budget and timeline goals.}
		\item {Instituted a real-time application and infrastructure monitoring and alerting framework for a large multimedia and entertainment corporation, boosting operational efficiency and minimizing downtime.}
		\item {Delivered high-availability storage area networks and VM platform design development and procurement reports for multiple universities and outreach centers spanning across multiple campuses.}
		\item {Devised comprehensive system and network specifications, integration, project management, and test plans for mergers and acquisitions, streamlining the entire process and ensuring seamless transitions.}
		\end{cvitems}}
	\cventry
	{Architect}
	{DexYP}
	{Dallas, TX}
	{2015-01-03 – 2017-12-31}
	{\begin{cvitems}
		\item {Collaborated effectively with all stakeholders to implement comprehensive threat detection and prevention strategies, incident response plans, forensic analysis, and data loss prevention measures.}
		\item {Designed and produced innovative enterprise solutions involving WAN/LAN, WLAN, Data Analytics, Security, and Virtual (e.g., NFV, SDN) technologies, developing automation rules and management policies to streamline processes and boost efficiency.}
		\item {Worked closely with the executive team to conduct risk assessments and develop business continuity plans to ensure compliance with SOX and PCI requirements.}
		\item {Collaborated with internal customers and corporate leadership to analyze, research, and implement enterprise-wide network and security architecture solutions that aligned with business objectives and goals.}
		\item {Designed and developed a custom open-source DCIM application that integrated internal infrastructure and application databases, enabling accurate inventory and physical location tracking across multiple data centers.}
		\item {Provided expert guidance to ensure emerging technologies and innovative ideas were aligned with the enterprise\textquotesingle{}s operational and strategic goals, helping to drive overall success and growth.}
		\item {As a technology liaison leader, facilitated collaboration and integration of impactful and advanced technical solutions to drive enterprise-wide transformation and success.}
		\end{cvitems}}
	\cventry
	{Executive Director, Network \& Telecom}
	{YP}
	{Glendale, CA}
	{2012-01-03 – 2015-12-31}
	{\begin{cvitems}
		\item {Reviewed the performance of network and telephony resources to determine operating costs, productivity levels, and necessary upgrades, ensuring optimal use of resources while minimizing expenses.}
		\item {Planned and executed business requirements, managed projects, and allocated resources effectively for network and telephony infrastructures, driving successful outcomes and meeting project goals and objectives.}
		\item {Defined and communicated project milestones, service level agreements, and resource allocation to all relevant stakeholders, including the executive team, department leads, support staff, and end-users, ensuring everyone was aligned with project objectives and timelines.}
		\end{cvitems}}
	\cventry
	{Associate Director, Voice \& Data}
	{AT\&T Interactive}
	{Dallas, TX}
	{2009-01-03 – 2012-12-31}
	{\begin{cvitems}
		\item {Presented compelling business case justifications and conducted thorough cost/benefit analyses for various operations spending and initiatives, ensuring informed decision-making by the executive team.}
		\item {Conducted benchmarking and analysis of the telephony and networking infrastructures to determine operating costs, productivity levels, and upgrade requirements, enabling informed resource allocation and strategic planning.}
		\item {Designed and implemented large-scale multi-vendor data and voice networks across multiple data centers, ensuring robust and scalable infrastructures that met business requirements and goals.}
		\item {Built and/or expanded six Tier 4 high-density data centers within the allocated budget and timeline, demonstrating strong project management skills and a deep understanding of data center technologies and requirements.}
		\end{cvitems}}
	\cventry
	{Manager, Network Operations}
	{Yellowpages.com \textbar{} AT\&T}
	{Dallas, TX}
	{2007-01-03 – 2009-12-31}
	{\begin{cvitems}
		\item {Provided oversight for all network operations, remote communications, wide and local area networks within multiple data centers, ensuring reliable and secure network connectivity across the enterprise.}
		\item {Maintained and managed operational metrics, goals, and project timelines, providing visibility and transparency into network performance and project progress to relevant stakeholders.}
		\item {Ensured high availability and full redundancy for all network infrastructures to achieve 99.9\% uptime, minimizing downtime and maintaining business continuity.}
		\item {Managed and delivered large-scale projects utilizing technical analysis, data network planning, engineering, and global infrastructure design experience, achieving project success and delivering value to the organization.}
		\end{cvitems}}
	\cventry
	{Director, Information Technology}
	{Curesearch \textbar{} National Childhood Cancer Foundation}
	{Baltimore, MD}
	{2004-01-03 – 2007-12-31}
	{\begin{cvitems}
		\item {Provided strategic oversight for infrastructure and data operations, ensuring alignment with the business and scientific objectives of the organization.}
		\item {Formulated and deployed long-term strategic plans for acquiring and enabling efficient and cost-effective information processing and communication technologies, ensuring that technology investments were aligned with organizational goals and priorities.}
		\item {Directed research on potential technology solutions and implementations in support of new initiatives, opportunities, and procurement efforts, providing informed recommendations to the executive team and relevant stakeholders.}
		\end{cvitems}}
	\cventry
	{Senior Network Engineer}
	{Yahoo! \textbar{} Overture Services \textbar{} Goto.com}
	{Pasadena, CA}
	{2001-01-03 – 2004-12-31}
	{\begin{cvitems}
		\item {Designed, integrated, and implemented networks and data centers across twelve countries, incorporating sales and customer service resources and production web-searching facilities, to enable efficient and scalable operations in multiple regions.}
		\item {Led the technology mergers and acquisitions migration and integration of FAST and AltaVista, ensuring seamless transitions and minimal disruption to operations.}
		\item {Collaborated with senior engineering team leads and executive management to develop technology and business roadmaps, providing efficient, scalable, cost-effective, and fault-tolerant network and systems infrastructures.}
		\item {Worked with project managers and internal customers to define proper deliverables, communicate expectations, and manage risks, ensuring timely delivery of milestones and objectives.}
		\end{cvitems}}
\end{cventries}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Cloud:  & {\skill{ AWS, Azure, Digital Ocean, CloudFlare}} \\
		Network Management:  & {\skill{ Solarwinds Orion, ManageEngine OpManager, Zabbix}} \\
		DevOps:  & {\skill{ Ansible \textbar{} Terraform, Github \textbar{} git, Docker \textbar{} Vagrant \textbar{} Multipass}} \\
		Collaboration \textbar{} Project Management:  & {\skill{ Asana, Notion, Trello, Smartsheet, Jira \textbar{} Confluence, Kanban \textbar{} Scrum}} \\
		Security:  & {\skill{ Fortigate, Cisco ASA, Rapid7}} \\
		Languages:  & {\skill{ Python, Javascript, PHP}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-7mm}

\cvsection{Awards}
\begin{cvhonors}
	\cvhonor
	{Cisco Certified Internetwork Expert (CCIE \#3406)}
	{CCIE Routing \& Switching, Written \& Lab}
	{Cisco Systems}
	{1997}
	\cvhonor
	{Cisco Certified Internetwork Expert (CCIE) Re-certification}
	{Security (2001), IP (2003), Routing \& Switching (2004,2007), VoIP (2009), Service Provider (2011), Data Center (2015)}
	{Cisco Systems}
	{}
	\cvhonor
	{AT\&T Service Excellence Award}
	{IPV6 Implementation}
	{AT\&T}
	{2011}
	\cvhonor
	{METRC Validated Software Provider}
	{CA Department of Food \& Agriculture \textbar{} CA Department of Public Health}
	{METRC}
	{2019}
	\cvhonor
	{Certified Enterprise Blockchain Professional (CEBP)}
	{101 Blockchains}
	{101 Blockchains}
	{2021}
\end{cvhonors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{BS in Computer Science and Engineering}
	{California State University, Long Beach}
	{}
	{1986 – 1992}
	{}
\end{cventries}

\vspace{-2mm}
\ 
\end{document}